Structured Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-10-10 R0V0.tex
Change counters, erase the fomulation of the set \mathscr{K} and reformulate the statement of the problem in consideration

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{corollary}[theorem]{Corollary}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Assumption}
\newtheorem{problem}[theorem]{Problem}

\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{example}[theorem]{Example}

@@

\begin{definition}\label{def:US}
	The system \eqref{eq:general system} is said to be \emph{universally stabilizable} with rate $\lambda$ if, for every forward complete solution $X^\ast(\cdot,\cdot,u^\ast)$ to \eqref{eq:general system}, there exists a static feedback law $k^\ast$ for system \eqref{eq:global exponential uniform stabilizability} rendering $X^\ast(\cdot,\cdot,u^\ast)$ globally exponentially uniformly stable with rate $\lambda$.
\end{definition}

For each component $i\in\mathbb{N}_{[1,m]}$ of the feedback law $k^\ast=(k_1^\ast,\ldots,k_m^\ast)^\top$, denote the set of indexes
\begin{equation*}
	\mathscr{K}(i)=\left\{j\in\mathbb{N}_{[1,n]}:k_i^\ast\ \text{depends explicitely on}\ x_j \right\}.
\end{equation*}
The definition of the set $\mathscr{K}(\cdot)$ encompasses different structures. For instance when $m=n$, full decentralization implies that, for each index $i\in\mathbb{N}_{[1,n]}$, the component $k_i^\ast$ of the function $k^\ast$ depends only on $x_i$. This is formalized by letting $\mathscr{K}(i)=\{i\}$. Moreover, at points where $k_i^\ast$ is differentiable, the explicit dependence on $x_i$ means that, for every index $j\in\mathbb{N}_{[1,n]}$ with $j\neq i$, $\partial k_i^\ast/\partial x_j\equiv0$.

Define also the set of feedback laws
\begin{align*}
	\Xi=\{k^\ast:\mathbb{R}_{\geq0}\times\mathbb{R}^n\to\mathbb{R}^m:\forall i\in\mathbb{N}_{[1,m]},k_i^\ast\ \text{depends on}\\
	 \text{the components of}\ x\ \text{with indexes given by}\ \mathscr{K}(i)\}.
\end{align*}

@@

\begin{problem}\label{problem formulation}\hfill
	\begin{enumerate}
		\item Find a feedback law rendering system \eqref{eq:general system} universally stable;

		\item The function $k^\ast$ belongs to the set $\Xi$.
		\end{enumerate}
\end{problem}

>>>>

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{claim}{Claim}
\newtheorem{corollary}{Corollary}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{problem}{Problem}

\theoremstyle{remark}
\newtheorem{remark}{Remark}
\newtheorem{example}{Example}

@@

\begin{definition}\label{def:US}
	The system \eqref{eq:general system} is said to be \emph{universally stabilizable} with rate $\lambda$ if, for every forward complete solution $X^\ast(\cdot,x^\ast,u^\ast)$ to \eqref{eq:general system}, there exists a static feedback law $k^\ast$ for system \eqref{eq:global exponential uniform stabilizability} rendering $X^\ast(\cdot,x^\ast,u^\ast)$ globally exponentially uniformly stable with rate $\lambda$.
\end{definition}

@@

\begin{problem}\label{problem formulation}
	For any forward complete solution $X^\ast(\cdot,x^\ast,u^\ast)$, find a feedback law $k^\ast$ such that, for every initial condition $x\in\mathbb{R}^n$, the issuing solution to  \eqref{eq:general system} in closed loop satisfies the inequality~\eqref{eq:global exponential uniform stabilizability}. Moreover, for each index $i\in\mathbb{N}_{[1,N]}$, the $i$-th component $k^\ast$ depends on specific components of $x$ that are collected into the set $\mathscr{K}(i)\subset\mathbb{N}_{[1,N]}$.
\end{problem}
